General constraints on magic distillation protocols from statistical mechanics

### 2021-06-04 magic_paper.tex
filled gaps, organised material within the new appendix, important to confirm that alpha = even/odd works: see Theorem 28 proof for explanation and numerical table

\begin{theorem} Let $\tau$ be in the interior of $\F$, and define $D_\infty(\rho,\tau) := D_\infty(W_\rho(\x) || W_\tau (\x))$. Then $D_\infty(\rho, \tau)$ is well-defined for all $\rho$, and the following hold:
\begin{enumerate}
\item $D_\infty(\rho, \tau) \ge 0$ for all quantum states $\rho$.
\item  $D_\infty(\rho , \tau) = 0$ if and only if $\rho =\tau$.
\item $D_\infty(\rho^{\otimes 2n}, \tau^{\otimes 2n}) = n D_\infty(\rho^{\otimes 2} ,\tau^{\otimes 2})$ for any $n \in \mathbb{N}$.
\item For any quantum state $\rho$, and any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$, we have $D_\infty (\rho , \tau) \ge D_\infty (\E(\rho), \E(\tau))$.
\end{enumerate}
\end{theorem}
\begin{proof}
	Since $\tau$ is in the interior of $\F$, its Wigner function obeys $W_\tau(\x) >0$ for all points $\x$ in the phase space. In general, $W_\rho(\x)$ is a quasi-distribution, however since $\sum_{\x} W_\rho (\x) = 1$ this implies it must have at least one positive component, so $\max_{\x} \frac{W_\rho(\x)}{W_\tau(\x)}>0$. Therefore $D_\infty (\rho,\tau)$ is always well-defined.

@@

We first define the classical $\alpha$-Renyi entropy in terms of the Wigner quasi-distribution of any state $\rho$ as
\begin{equation}
	H_\alpha(\rho) := \frac{1}{1-\alpha} \log \sum_{\bmx} W_{\rho}(\bmx)^\alpha,
\end{equation}
where $\alpha$ can take values of the form $\alpha_1 / \alpha_2$, with even $\alpha_1 \geq 0$ and odd $\alpha_2 > 0$.
Note that for any quantum state $\rho$, $H_1$ in particular is not well-defined, while for any valid $\alpha$ we have that
\begin{equation}
	H_0(\rho) = 2\log_2 d = H_\alpha \left( \id/d \right),
\end{equation}
where $d$ is the dimension of $\rho$.
For $\rho = \rho_{\rm{S}}(\epsilon)$, we get
\begin{equation}
	H_{\alpha}\left(\rho_{\rm{S}}(\epsilon)\right) = \frac{1}{1-\alpha}\log_2 \left[ 8\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^\alpha + \left(-\frac{1}{3} + \frac{4}{9}\epsilon \right)^\alpha \right]
\end{equation}

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.35]{figs/test/H_vs_eps_a.pdf}
    \caption{\ddd{[TO DO: Set $\epsilon = 0$ and determine region of $\alpha$ such that $H <0$.]} Here, the exponent is $\alpha = even/odd$ for $1.10 \leq \alpha \leq 1.50$. First dashed contour from the right corresponds to $H_\alpha(\rho_{\rm{S}}(0)) = 0$.
    }
    \label{fig:lcs}
\end{figure}

@@

\begin{theorem}\label{thm:HSchur}
	Let $\w, \w' \in \mathbb{R}^N$ be quasi-distributions such that $\w \succ \w'$.
	Then, $H_\alpha(\w) \leq H_\alpha(\w')$, where $\alpha = \frac{2a}{2b+1}$ for any positive integers $a,b$ with $a > b$.
\end{theorem}
\begin{proof}
We have $\alpha = \frac{2a}{2b+1} \geq \frac{2b+2}{2b+1} > 1$ and $\alpha$ is a rational with even numerator and odd denominator, so $\sum_i x_i^\alpha > 0$ and $H_\alpha(\x)$ is well-defined for all quasi-distributions $\x$.

@@

Consider the partial derivatives
\begin{equation}
	\frac{\partial H_\alpha}{\partial w_i} = \frac{\alpha}{(\alpha-1)\sum_k{w_k^\alpha}}(-w_i^{\alpha-1})
\end{equation}
Whenever $w_i \geq w_j$, for $\alpha$ in the given form, we always have that $\alpha - 1$ is positive and of the form odd$/$odd so \nick{expand argument}
\begin{equation}
	-w_i^{\alpha-1} \leq -w_j^{\alpha-1},
\end{equation}
which leads to
\begin{equation}
	\frac{\partial H_\alpha}{\partial w_i} \leq \frac{\partial H_\alpha}{\partial w_j}.
\end{equation}
Therefore, $H_\alpha$ is Schur-concave and
\begin{equation}
	H_\alpha(\w) \leq H_\alpha(\w'),
\end{equation}
for any quasi-distributions $\w, \w'$.
\end{proof}
Note that if $\alpha < 1$ or is of the form odd$/$even, the argument of~\cref{thm:HSchur} does not hold.

We can now derive the following entropic bounds on magic state transformations.
\begin{theorem}
	Consider a general magic state distillation process $\rho^{\otimes n} \rightarrow \rho'^{\otimes n'}$	in the unital fragment.
	We have the following family of upper bounds on the distillation rate $R := n'/n$,
	\begin{equation}
		R \leq \frac{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho \right)}{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho') \right)},
	\end{equation}
	where $\hspace{-1pt}\alpha\hspace{-1pt}$ is such that $\hspace{-1pt}H_\alpha(\sigma)\hspace{-2pt}$ is well-defined for all states $\sigma$.
\end{theorem}
\begin{proof}
	We can regularise the number of output copies in the state distillation by tensoring in $(n-n')$ copies of the (free) maximally mixed state $\id/3$, so that we instead consider the process
\begin{equation}
	\rho^{\otimes n} \rightarrow \rho'^{\otimes n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes (n - n')}.
\end{equation}
Since we have that $W_{\rho^{\otimes n}}(\bmx) \succ_{\id/3} W_{\rho'^{\otimes n'}}(\bmx)$, by Schur-concativity of $H_\alpha$ we obtain
\begin{equation}
	H_\alpha \left( \rho^{\otimes n} \right) \leq H_\alpha \left( \rho'^{\otimes n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes (n - n')} \right).
\end{equation}
By additivity of $H_\alpha$, we can rewrite the inequality as
\begin{equation}
	n H_\alpha \left( \rho \right) \leq n' H_\alpha \left( \rho' \right) + (n - n') H_\alpha \left( \id/3 \right).
\end{equation}
Now, $H_\alpha \left( \id/3 \right)$ is the maximum value of $H_\alpha(\rho)$ for unital processes because every state $\rho$ majorizes $\id/3$, so we can finally re-arrange the inequality to
\begin{equation}
	\frac{n'}{n} \leq \frac{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho \right)}{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho' \right)}.
\end{equation}
\end{proof}

@@

\ddd{[TO-DO AND TIDY AND CHECK]} The extension of the domain of the Renyi entropies to real values means that is it not real-valued for certain values of $\alpha$. However we can make $H_\alpha(\w)$ well-defined on the whole of $\mathcal{Q}$ if $\alpha = \frac{a}{b}$ where $b$ is an odd integer, and $a$ is an even integer. Depending on the set of quasi-distributions the quantum system supports the restriction of $a$ being even could be lifted, provided that the sum $\sum_i w_i^\alpha >0$, however we do not consider this here, and restrict to the assumption that $a$ is even.

\begin{theorem} The functions $H_\alpha(\w)$ are well-defined on $\mathcal{Q}$ for $\alpha = \frac{a}{b}$ with $a$ an even integer and $b$ an odd integer, and are Schur-concave functions.
\end{theorem}
\begin{proof}
We now make use of the Schur-Ostrowski criterion to determine when $H_\alpha$ is Schur-Convex on $\mathcal{Q}$.

We have that
\begin{align}
V_k:=-\frac{\partial H_\alpha}{\partial w_k} &= \partial_k \frac{1}{\alpha-1} \log \sum_i w_i^{\alpha} \\
&= \frac{1}{(\alpha-1) \sum_i w_i^{\alpha}}\alpha w_k^{\alpha-1}.
\end{align}
We now impose the monotonicity condition $V_1 \ge V_2 \ge V_3 \cdots \ge V_N$. This requires, setting $S= \sum_i w_i^\alpha$ for simplicity, that
\begin{align}
 \frac{1}{(\alpha-1)S}\alpha w_i^{\alpha-1}\ge \frac{1}{(\alpha-1)S}\alpha w_{i+1}^{\alpha-1},
\end{align}
for each $i=1,2,\dots, N-1$. We have that $S >0$, since $a$ is even, and assume that $\alpha >1$ so that
\begin{equation}
w_i^{\alpha-1}\ge w_{i+1}^{\alpha-1}\mbox{ for all } 1 \le i < N.
\end{equation}
For $\alpha = a/b > 1$ we have $\alpha-1 = (a-b)/b = a'/b >0$ where $a'$ is an even integer and $b$ an odd integer. We now assume that $\w \in \mathcal{Q}^\downarrow$ so that $ w_i \ge w_{i+1}$. \ddd{[Wait I'm not sure the inequalities work...]} \nick{Look at proof of~\cref{thm:HSchur} and table below}

\begin{table}[h]
  \def\arraystretch{1.5}
  \centering
  \begin{tabular}{c|c|c|c||c|c}
    $w_i$ & $w_{i+1}$ & $\alpha$ & $\frac{w_i^{\alpha-1}}{\alpha-1} \geq \frac{w_{i+1}^{\alpha-1}}{\alpha-1}$ & $\alpha$ & $\frac{w_i^{\alpha-1}}{\alpha-1} \geq \frac{w_{i+1}^{\alpha-1}}{\alpha-1}$ \\[0.5ex]\hline
    $2$ & $1.5$  & $3$ & $2 > 1.125$ T & $1/3$ & $-0.94 > -1.14$ T \\
    $2$ & $-1.5$ & $3$ & $2 > 1.125$ T & $1/3$ & $-0.94 > -1.14$ T \\
    $2$ & $-2.5$ & $3$ & $2 < 3.125$ F & $1/3$ & $-0.94 < -0.81$ F \\[0.5ex]\hline
    $2/3$ & $1/3$  & $3$ & $0.22 > 0.06$ T & $1/3$ & $-1.97 > -3.12$ T \\
    $2/3$ & $-1/3$ & $3$ & $0.22 > 0.06$ T & $1/3$ & $-1.97 > -3.12$ T \\
    $2/3$ & $-4/3$ & $3$ & $0.22 < 0.89$ F & $1/3$ & $-1.97 < -1.24$ F \\[0.5ex]\hline
    $2$ & $1.5$  & $4$ & $2.67 > 1.125$ T & $2/3$ & $-2.38 > -2.62$ T \\
    $2$ & $-1.5$ & $4$ & $2.66 > -1.125$ T & $2/3$ & $-2.38 > 2.62$ F \\
    $2$ & $-2.5$ & $4$ & $2.66 > 5.21$ T & $2/3$ & $-2.38 > 2.21$ F \\
    $-2$ & $-2.5$ & $4$ & $-2.66 > -5.21$ T & $2/3$ & $2.38 > 2.21$ T \\[0.5ex]\hline
    $2/3$ & $1/3$  & $4$ & $0.10 > 0.01$ T & $2/3$ & $-3.43 > -4.33$ T \\
    $2/3$ & $-1/3$ & $4$ & $0.10 > -0.01$ T & $2/3$ & $-3.43 > 4.33$ F \\
    $2/3$ & $-4/3$ & $4$ & $0.10 > -0.79$ T & $2/3$ & $-3.43 > 2.73$ F \\
    $-1/3$ & $-2/3$ & $4$ & $-0.01 > -0.10$ T & $2/3$ & $4.33 > 3.43$ T \\
    $-1/3$ & $-4/3$ & $4$ & $-0.01 > -0.79$ T & $2/3$ & $4.33 > 2.73$ T
  \end{tabular}
  \caption{Exploring in what regimes the Schur-Ostrowski criterion holds.}
  \label{tab:test}
\end{table}

@@

This is probably all we need to show:
\begin{equation}
H_\alpha(\Gamma_{\mathbf{a}}(\p)) = D_\alpha(\p ||\r),
\end{equation}
where we define the Renyi relative entropy
\begin{equation}
D_\alpha (\p || \r) := \frac{1}{\alpha -1} \log \sum_i p_i^\alpha q_i^{1-\alpha}.
\end{equation}
This probably follows from the details of how the $\Gamma_{\mathbf{a}}$ relates to $\r$. Needs expanding carefully.
\subsection{Dropping pre/post-processing of the magic states}
\label{app:cliff_processing}

>>>>

\begin{theorem} Let $\tau$ be in the interior of $\F$, and define $D_\infty(\rho,\tau) := D_\infty(W_\rho(\x) || W_\tau (\x))$. Then $D_\infty(\rho, \tau)$ is well-defined for all $\rho$, and the following hold: \nick{can generalise to $D_{\alpha}$ for appropriate $\alpha$}
\begin{enumerate}
\item $D_\infty(\rho, \tau) \ge 0$ for all quantum states $\rho$.
\item  $D_\infty(\rho , \tau) = 0$ if and only if $\rho =\tau$.
\item $D_\infty(\rho^{\otimes 2n}, \tau^{\otimes 2n}) = n D_\infty(\rho^{\otimes 2} ,\tau^{\otimes 2})$ for any $n \in \mathbb{N}$.
\item For any quantum state $\rho$, and any free operation $\E$ such that $\E(\tau)$ is in the interior of $\F$, we have $D_\infty (\rho , \tau) \ge D_\infty (\E(\rho), \E(\tau))$.
\end{enumerate}
\end{theorem}
\begin{proof}
	Since $\tau$ is in the interior of $\F$, its Wigner function obeys $W_\tau(\x) >0$ for all points $\x$ in the phase space. In general, $W_\rho(\x)$ is a quasi-distribution, however since $\sum_{\x} W_\rho (\x) = 1$ this implies it must have at least one positive component, so $\max_{\x} \frac{W_\rho(\x)}{W_\tau(\x)}>0$. Therefore $D_\infty (\rho,\tau)$ is always well-defined.

@@

We first define the classical $\alpha$-Renyi entropy in terms of the Wigner quasi-distribution of any state $\rho$ as
\begin{equation}
	H_\alpha(\rho) := \frac{1}{1-\alpha} \log \sum_{\bmx} W_{\rho}(\bmx)^\alpha,
\end{equation}
where $\alpha$ can take values of the form $2a / (2b+1)$, for non-negative integers $a,b$ to ensure that the argument of the logarithm is positive.
Note that for any quantum state $\rho$, $H_1(\rho)$ in particular is not well-defined  \nick{Notation clashes with quantum Renyi entropies}, while for any valid $\alpha$ we have that
\begin{equation}
	H_0(\rho) = 2\log_2 d = H_\alpha \left( \id/d \right),
\end{equation}
where $d$ is the dimension of $\rho$.
For $\rho = \rho_{\rm{S}}(\epsilon)$, we get
\begin{equation}
	H_{\alpha}\left(\rho_{\rm{S}}(\epsilon)\right) = \frac{1}{1-\alpha}\log_2 \left[ 8\left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^\alpha + \left(-\frac{1}{3} + \frac{4}{9}\epsilon \right)^\alpha \right]
\end{equation}

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.35]{figs/test/H_vs_eps_a.pdf}
    \caption{\ddd{[TO DO: Set $\epsilon = 0$ and determine region of $\alpha$ such that $H <0$.]} Here, the exponent is $\alpha =$ even$/$odd for $1.10 \leq \alpha \leq 1.50$. $H_\alpha$ is increasing in $\alpha$ and $\epsilon$ \nick{should be easy to show analytically}. First dashed contour from the right corresponds to $H_\alpha(\rho_{\rm{S}}(\epsilon)) = 0$. Specifically, $H_\alpha(\rho_{\rm{S}}(0)) = 0$ has a unique solution, which is the \nick{probably irrational - this seems problematic} solution of $3^\alpha - 2^{3-\alpha} = 1$.
    }
    \label{fig:lcs}
\end{figure}

@@

\ddd{[TO-DO TIDY AND CHECK]}
\begin{theorem}\label{thm:HSchur}
	Let $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$.
	Then, $H_\alpha$ is Schur-concave, i.e. for quasi-distributions $\w, \w' \in \mathbb{R}^N$, we have $H_\alpha(\w) \leq H_\alpha(\w')$, whenever $\w \succ \w'$.
\end{theorem}
\begin{proof}
We have $\alpha = \frac{2a}{2b+1} \geq \frac{2b}{2b-1} > 1$ and $\alpha$ is a rational with even numerator and odd denominator, so $\sum_i x_i^\alpha > 0$ and $H_\alpha(\x)$ is well-defined for all quasi-distributions $\x$.

@@

Consider the partial derivatives
\begin{equation}
	\frac{\partial H_\alpha}{\partial w_i} = \frac{\alpha}{(\alpha-1)\sum_k{w_k^\alpha}}(-w_i^{\alpha-1}).
\end{equation}
Whenever $w_i \geq w_j$, for $\alpha$ in the given form, we always have that $\alpha - 1$ is positive and of the form odd$/$odd so \nick{expand argument}
\begin{equation}
	-w_i^{\alpha-1} \leq -w_j^{\alpha-1},
\end{equation}
which leads to
\begin{equation}
	\frac{\partial H_\alpha}{\partial w_i} \leq \frac{\partial H_\alpha}{\partial w_j}.
\end{equation}
Therefore, $H_\alpha$ is Schur-concave and
\begin{equation}
	H_\alpha(\w) \leq H_\alpha(\w'),
\end{equation}
for any quasi-distributions $\w, \w'$.

\begin{table}[h]
  \def\arraystretch{1.5}
  \centering
  \begin{tabular}{c|c|c|c||c|c}
    $w_i$ & $w_{i+1}$ & $\alpha$ & $\frac{w_i^{\alpha-1}}{\alpha-1} \geq \frac{w_{i+1}^{\alpha-1}}{\alpha-1}$ & $\alpha$ & $\frac{w_i^{\alpha-1}}{\alpha-1} \geq \frac{w_{i+1}^{\alpha-1}}{\alpha-1}$ \\[0.5ex]\hline
    $2$ & $1.5$  & $3$ & $2 > 1.125$ T & $1/3$ & $-0.94 > -1.14$ T \\
    $2$ & $-1.5$ & $3$ & $2 > 1.125$ T & $1/3$ & $-0.94 > -1.14$ T \\
    $2$ & $-2.5$ & $3$ & $2 < 3.125$ F & $1/3$ & $-0.94 < -0.81$ F \\[0.5ex]\hline
    $2/3$ & $1/3$  & $3$ & $0.22 > 0.06$ T & $1/3$ & $-1.97 > -3.12$ T \\
    $2/3$ & $-1/3$ & $3$ & $0.22 > 0.06$ T & $1/3$ & $-1.97 > -3.12$ T \\
    $2/3$ & $-4/3$ & $3$ & $0.22 < 0.89$ F & $1/3$ & $-1.97 < -1.24$ F \\[0.5ex]\hline
    $2$ & $1.5$  & $4$ & $2.67 > 1.125$ T & $2/3$ & $-2.38 > -2.62$ T \\
    $2$ & $-1.5$ & $4$ & $2.66 > -1.125$ T & $2/3$ & $-2.38 > 2.62$ F \\
    $2$ & $-2.5$ & $4$ & $2.66 > 5.21$ T & $2/3$ & $-2.38 > 2.21$ F \\
    $-2$ & $-2.5$ & $4$ & $-2.66 > -5.21$ T & $2/3$ & $2.38 > 2.21$ T \\[0.5ex]\hline
    $2/3$ & $1/3$  & $4$ & $0.10 > 0.01$ T & $2/3$ & $-3.43 > -4.33$ T \\
    $2/3$ & $-1/3$ & $4$ & $0.10 > -0.01$ T & $2/3$ & $-3.43 > 4.33$ F \\
    $2/3$ & $-4/3$ & $4$ & $0.10 > -0.79$ T & $2/3$ & $-3.43 > 2.73$ F \\
    $-1/3$ & $-2/3$ & $4$ & $-0.01 > -0.10$ T & $2/3$ & $4.33 > 3.43$ T \\
    $-1/3$ & $-4/3$ & $4$ & $-0.01 > -0.79$ T & $2/3$ & $4.33 > 2.73$ T
  \end{tabular}
  \caption{\nick{NUMERICS ON SCHUR-OSTROWSKI CONDITION} Seems like $\alpha=$ even$/$odd and $\alpha > 1$ works for any combination of $w_i, w_{i+1}$ with $w_i > w_{i+1}$ and seems also that no other case works.}
  \label{tab:test}
\end{table}

\end{proof}
Note that if $\alpha < 1$ or is of the form odd$/$even, the argument of~\cref{thm:HSchur} does not hold.
However, the set $F := \{2a/(2b+1): a,b \in \mathbb{N} \text{ and } a>b\}$ is dense in the rationals $\mathbb{Q}_{>1}$ (which in turn is dense in $\mathbb{R}_{>1}$) as any rational $c/d$ with $c>d$ can be approximated by a sequence $f_n := c2^n / (d2^n+1)$ with every element $f_n$ in the set $F$. \nick{can turn into lemma}

We can now derive the following entropic bounds on magic state transformations.
\begin{theorem}
	Consider a general magic state distillation process $\rho^{\otimes n} \rightarrow \rho'^{\otimes n'}$	in the unital fragment.
	We have the following family of upper bounds on the distillation rate $R := n'/n$,
	\begin{equation}
		R \leq \frac{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho \right)}{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho') \right)} = \frac{D_{\alpha}(\rho||\id/3)}{D_{\alpha}(\rho'||\id/3)},
	\end{equation}
	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$.
\end{theorem}
\begin{proof}
	For the given form of $\alpha$, $H_\alpha(\sigma)$ is well-defined adn Schur-concave for all quantum states $\sigma$.

	We first regularise the number of output copies in the state distillation by tensoring in $(n-n')$ copies of the (free) maximally mixed state $\id/3$, so that we instead consider the process
\begin{equation}
	\rho^{\otimes n} \rightarrow \rho'^{\otimes n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes (n - n')}.
\end{equation}
Since we have that $W_{\rho^{\otimes n}}(\bmx) \succ_{\id/3} W_{\rho'^{\otimes n'}}(\bmx)$, by Schur-concativity of $H_\alpha$ we obtain
\begin{equation}
	H_\alpha \left( \rho^{\otimes n} \right) \leq H_\alpha \left( \rho'^{\otimes n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes (n - n')} \right).
\end{equation}
By additivity of $H_\alpha$, we can rewrite the inequality as
\begin{equation}
	n H_\alpha \left( \rho \right) \leq n' H_\alpha \left( \rho' \right) + (n - n') H_\alpha \left( \id/3 \right).
\end{equation}
Now, $H_\alpha \left( \id/3 \right)$ is the maximum value of $H_\alpha(\rho)$ for unital processes because every state $\rho$ majorizes $\id/3$, so we can finally re-arrange the inequality to
\begin{equation}
	\frac{n'}{n} \leq \frac{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho \right)}{H_\alpha \left( \id/3 \right) - H_\alpha \left( \rho' \right)}.
\end{equation}
\end{proof}

@@

@@

This is probably all we need to show:
\begin{equation}
H_\alpha(\Gamma_{\mathbf{a}}(\p)) = D_\alpha(\p ||\r),
\end{equation}
where we define the Renyi relative entropy
\begin{equation}
D_\alpha (\p || \r) := \frac{1}{\alpha -1} \log \sum_i p_i^\alpha q_i^{1-\alpha}.
\end{equation}
This probably follows from the details of how the $\Gamma_{\mathbf{a}}$ relates to $\r$. Needs expanding carefully.

\begin{theorem}
	Consider a general magic state distillation process that converts magic state $\rho^{\otimes n} \longrightarrow \rho'^{\otimes n'}$ as well as equilibrium state $\tau^{\otimes n} \longrightarrow \tau'^{\otimes n'}$, where we assume that $W_{\tau^{\otimes n}}(\bmx) = a_{\bmx}/K$ and $W_{\tau'^{\otimes n'}}(\bmx) = a_{\bmx}/K$ for positive integers $a_{\bmx}, a_{\bmx}'$ and $K = \sum_{\bmx} a_{\bmx} = \sum_{\bmx} a_{\bmx}'$.

	We have the following family of upper bounds on the distillation rate $R := n'/n$,
	\begin{equation}
		R \leq \text{\nick{BOUND}},
	\end{equation}
	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$.
\end{theorem}
\begin{proof}
	For the sake of clarity, we write $\rho_n \coloneqq \rho_S(\epsilon)^{\otimes n}$, $\rho'_{n'} \coloneqq \rho_S(\epsilon')^{\otimes n'}$, $\tau_n \coloneqq \tau^{\otimes n}$ and $\tau'_{n'} \coloneqq \tau'^{\otimes n'}$.

	We have that $(W_{\rho_n}, W_{\tau_n}) \succ W_{\rho'_{n'}}, W_{\tau'_{n'}})$, or equivalently $\Gamma_{\bma}(W_{\rho_n}) \succ \Gamma_{\bma'}(W_{\rho'_{n'}})$, where
\begin{align}
	\Gamma_{\bma}(W_{\rho_n}) &= \bigoplus_{\bmx} W_{\rho_n}(\bmx) \left(\frac{1}{KW_{\tau_n}(\bmo)}, \dots, \frac{1}{KW_{\tau_n}((d,d))} \right)\nonumber\\
	&= \frac{1}{K}\bigoplus_{\bmx}\bigoplus_{\bmy} \frac{W_{\rho_n}(\bmx)}{W_{\tau_n}(\bmy)},
\end{align}
and similarly for $\Gamma_{\bma'}(W_{\rho'_{n'}})$.
Therefore,
\begin{equation}
	H_{\alpha}(\Gamma_{\bma}(W_{\rho_n})) = \frac{1}{1-\alpha} \log_2 \left( \frac{1}{K^\alpha} \sum_{\bmx, \bmy} \frac{W_{\rho_n}(\bmx)^\alpha}{W_{\tau_n}(\bmy)^\alpha} \right),
\end{equation}
while
\begin{equation}
	D(\rho||\tau) = \frac{1}{\alpha-1} \log_2 \sum_{\bmx,\bmy} \frac{W_{\rho}(\bmx)^\alpha}{W_{\tau}(\bmy)^{\alpha-1}}.
\end{equation}
\nick{correct mistakes, bridge gaps}
\end{proof}

\subsection{Dropping pre/post-processing of the magic states}
\label{app:cliff_processing}
